---
title: "PSY 8712 Week 8 Project"
author: "Taylor Knickel"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link]().
An interactive web app is available by [clicking this link instead]().

# **Script Settings and Resources**
```{r, message = FALSE, warning = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(dplyr)
library(ggplot2)
library(stringr)
library(kableExtra)
```

# **Data Import and Cleaning**
This chunk imports the dataset and creates a clean version as a tibble that includes a reversed code version of q5 and relocating the column to the correct location. This was needed in order to accurately calculate mean scores and data visualization in later sections. 
```{r}
week8_tbl <- read.csv("../data/week3.csv", header = TRUE) %>%
  mutate(Q5 = as.integer(6 - q5)) %>%
  select(-q5) %>%
  rename(q5 = Q5) %>%
  relocate(q5, .after = q4)
```

# **Visualization**
This chunk first displays the data within q1 to q6, and then includes a scatterplot of the mean scores of q1 to q6 on the x-axis and the mean scores of q8 to q10 on the y-axis. The scatterplot also includes a purple OLS regression line with a shaded error band that displays the confidence interval around the OLS line.
```{r, echo = FALSE}
week8_tbl %>%
  select(q1:q6) %>%
  kableExtra::kable()
week8_tbl <- week8_tbl %>%
  mutate(mean_x = rowMeans(select(., q1:q6), na.rm = TRUE),
         mean_y = rowMeans(select(., q8:q10), na.rm = TRUE))
  ggplot(week8_tbl, aes(x = mean_x, y = mean_y)) +
  geom_point() +
  geom_smooth(method = "lm", color = "purple", fill = "purple") +
  labs(x = "Mean Scores of Q1-Q6", y = "Mean Scores of Q8-Q10")
```

# **Analysis**
This chunk performs a correlation test using the mean scores from q1 to q6 and mean scores from q8 to q10 data. The output displays the correlation (r value) and p-value from the correlation test. 
```{r}
cor_list <- cor.test(week8_tbl$mean_x, week8_tbl$mean_y)

cor_list$estimate
cor_list$p.value

rvalue_chr <- str_replace(as.character(round(cor_list$estimate, 2)), "^0", "")
```
The correlation observed is `r rvalue_chr`. The p-value is `r cor_list$p.value`, which is greater than the conventional alpha/significance level of 0.05, so we fail to reject the null hypothesis that there is no correlation between mean scores from questions 1 to 6 and mean scores from questions 8 to 10. 

# **Data Export**
This chunk exports a "skinny" version of the dataset, which only includes columns q1 to q10 and the mean_x and mean_y columns as this is what is necessary to run the code. The exported version is saved as an RDS file, as this is useful for creating a shiny app. 
```{r}
week8_tbl %>%
  select(q1:q10, mean_x, mean_y) %>%
  saveRDS("../shiny/week8.rds")
```
